### 2014-09-06 guarantee.tex
guarantee typos fixed

\begin{mytheorem}[Soundness]
The trace computed by the solver,  $\tau'=<\Gamma , \{\tau_{t_1}, \tau_{t_2}, \dots \tau_{t_n} \}, O', \theta'>$, is a feasible trace for the concurrent program, where $O'$ defines its schedule and $\theta'$ defines the value mapping.
\end{mytheorem}

\begin{proof}
The proof consists of two parts: (1) the trace is feasible, and (2) the trace can be generated by the program. We sketch the proof as follows.
\begin{itemize}
\item  $\tau'$ is feasible. Researchers~\cite{chao,maximal} point out a 
trace is feasible iff it satisfies the sequential consistency, 
i.e., $\forall object\ o, \tau'\downarrow_{o}$ satisfies the serial 
specification of the object $o$. If  all the events considered are of 
the types in Table~\ref{Ta:syntax}, then the sequential consistency 
precisely means the following: (1) read-write consistency, i.e., each 
read event of a variable should contain the value written by the most 
recent write event, and (2) the synchronization consistency, e.g., the 
acquisition and release of a lock should not interleave with other 
lock operations of the same lock, the start event of a thread should 
follow the fork event of the parent thread. Our inter-thread data 
flow constraints guarantee the read-write consistency among shared 
locations. The SSA form encodes the read-write consistency among local 
variables. The synchronization consistency is also captured as constraints 
in our solver. 
\item $\tau$ can be generated by the program, i.e., for each 
thread $t$, $\tau'\downarrow_{t}$ can be generated by the corresponding 
thread code. This claim requires that,  for any two adjacent 
events $e$ and $e'$ in  $\tau'\downarrow_{t}$, (1) if $e$ is not a 
branch, $inst^e$ and $inst^{e'}$ should be adjacent in the code; (2) 
if $e$ is a branch, $inst^e$ and $inst^{e'}$ should be adjacent in terms
of control flow and the $inst^e$ should be evaluated as the boolean 
value implied by $inst^{e'}$. We derive the trace  through either 
concrete execution or precise modeling of unexplored branches, 
which satisfies the requirements and guarantees the correctness of the claim.
\end{itemize}
\end{proof}

\begin{mydiscussion}[Detection Capability]
Our technique has stronger detection capability than existing techniques~\cite{yannis,jeff, said}.
\end{mydiscussion}

>>>>

\begin{mytheorem}[Soundness]
The trace $\tau'$ computed by the solver is a feasible trace for the concurrent program.
\end{mytheorem}

\begin{proof}\let\qed\relax
The proof consists of two parts: (1) the trace is feasible, and (2) the trace can be generated by the program. We sketch the proof as follows.
\begin{itemize}
\item  $\tau'$ is feasible. Researchers~\cite{chao,maximal} point out a 
trace is feasible iff it satisfies the sequential consistency, 
i.e., $\forall object\ o, \tau'\downarrow_{o}$ satisfies the serial 
specification of the object $o$. If  all the events considered are of 
the types in Table~\ref{Ta:syntax}, then the sequential consistency 
precisely means the following: (1) read-write consistency, i.e., each 
read event of a variable should contain the value written by the most 
recent write event, and (2) the synchronization consistency, e.g., the 
acquisition and release of a lock should not interleave with other 
lock operations of the same lock, the start event of a thread should 
follow the fork event of the parent thread. Our inter-thread data 
flow constraints guarantee the read-write consistency among shared 
locations. The SSA form encodes the read-write consistency among local 
variables. The synchronization consistency is also captured as constraints 
in our solver. 
\item $\tau'$ can be generated by the program, i.e., for each 
thread $t$, $\tau'\downarrow_{t}$ can be generated by the corresponding 
thread code. This claim requires that,  for any two adjacent 
events $e$ and $e'$ in  $\tau'\downarrow_{t}$, (1) if $e$ is not a 
branch, $inst^e$ and $inst^{e'}$ should be adjacent in the code; (2) 
if $e$ is a branch, $inst^e$ and $inst^{e'}$ should be adjacent in terms
of control flow and the $inst^e$ should be evaluated as the boolean 
value implied by $inst^{e'}$. We derive the trace  through either 
concrete execution or precise modeling of unexplored branches, 
which satisfies the requirements and guarantees the correctness of the claim.
\end{itemize}
\end{proof}

\begin{mydiscussion}[Detection Capability]
Our technique has stronger detection capability than existing techniques~\cite{yannis,pldi14,Said:2011}.
\end{mydiscussion}
